### 2017-02-12 Dissertation/Latex/head/acknowledgements.tex
updated acknowledgement

The writing and completion of this dissertation would not have been possible without the assistance, support, and guidance of the many special people in my life. Firstly, I would like to thank God for giving me the capability to contribute to the engineering world and hopefully assist the future civilizations in creating technologies for the good of mankind. Technology has been abused by the powers that be, and I hope that, someday, ethical values will be the priorities of our future leaders in order to sustain peace and harmony in this planet.

>>>>

The writing and completion of this dissertation would not have been possible without the assistance, support, and guidance of the many special people in my life. Firstly, I would like to thank God for giving me the capability to contribute to the engineering world and hopefully assist the future civilizations in creating technologies for the good of mankind. I hope that ethical values will be exercised and that the technologies arising from the new frontiers of science are used in conscientious manners.
